---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)

```

```{r}
library(dplyr)
```

```{r}
library(readr)
cake <- read_csv("~/Documents/codeclan/dirty_data_codeclan_project_mujtaba/dirty_data_mujtaba_project/task_01/clean_data/cake.csv")
View(cake)
```


#start the analysis of clean data to a new file, ready for analysis

# Data Analysis

#Q1 Which cake has the most cocoa in it? 


```{r}
cake %>% 
  filter(ingredient == "Cocoa") %>% 
arrange(desc(quantity)) %>% 
  head(1)
```

#Q2 For sponge cake, how many cups of ingredients are used in total? 

# Sponge exists in the cake variable as "Sponge". Sponge cake ingredients that come in cup measurements can be filtered and then totalled

```{r}
cake %>% 
  filter(Cake == "sponge") %>% 
 filter(measure == "cup") %>% 
   summarise(cup = sum(quantity))
```

#Q3 How many ingredients are measured in teaspoons?


#This can be found by first filtering for "teaspoon" in the measure column. then counting the distinct rows.


```{r}
cake %>% 
  filter(measure == "teaspoons") %>% 
  distinct(ingredient) %>%
  pull()
 
```





#Q4 Which cake has the most unique ingredients?

#This can be found by first grouping by cake and then using distinct() to count only distinct ingredients in each cake.


```{r}
cake %>% 
  group_by(Cake) %>% 
  summarise(numb_ingredient = n()) %>% 
  arrange(desc(numb_ingredient))
```




#5 Which ingredients are used only once?

#This can be found by group the ingredient and summrise the number  of each ingrediant. 
```{r}
cake %>% 
  group_by(ingredient) %>% 
  summarise(numb_ = n()) %>% 
filter(numb_cake == 1)
```
```{r}
cake %>% 
  filter(numb_cakes == 1)
```

